Deep Reinforcement Learning \\ Actor-Critic and Trust region-based

### 2021-01-13 Paper/Paper.tex
error in advantage actor critic pseudocode corrected
added explanation for critic rule update

\noindent This interaction  is an example of a Markov Decision Process (MDP)\cite{Sutton1998} $\mathcal{M}=(\mathcal{S}, \mathcal{A}, P, R)$, where:

@@

Now that we have (more or less) a clear idea of what RL seeks (maximize the return $G$) and how to do it (by finding an optimal policy $\pi$), we need to define a way to quantify how good a state $a$ is (in terms of the return $G$) in a given environment (when we follow a policy $\pi$), and how good an action $a$ is (in terms of the return $G$) when the environment is in state $s$ (and when we follow a policy $\pi$). This is done through the \emph{State-value} and \emph{Action-value} functions respectively:
\begin{itemize}
    \item \textbf{State-value}: $V_{\pi}(s):= \mathbb{E}_{\pi}[G_t|s_t=s]$.
    \item \textbf{Action-value}: $Q_{\pi}(s, a):= \mathbb{E}_{\pi}[G_t|s_t=s, a_t=a]$.
\end{itemize}

@@

\begin{equation}
  \resizebox{.91\linewidth}{!}{%
  $
    \boldsymbol{\theta}_{t+1} = \boldsymbol{\theta}_{t} + \alpha (R_{t+1} + \gamma V(S_{t+1};\boldsymbol{w}) - V(S_{t};\boldsymbol{w})) \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}
  $
  }
  \label{eq:learn_rule_4}
\end{equation}

A pseudocode for an algorithm which uses rule \ref{eq:learn_rule_4} is shown in \ref{alg:A2C}.

%\resizebox{.95\linewidth}{!}{%
\begin{algorithm}[h]
 \textbf{Input}: differentiable policy and state-value function parameterization $\pi(a|s;\boldsymbol{\theta})$ and $V(s;|s;\boldsymbol{w})$\;
 \textbf{Parameters}: step sizes $\alpha^{\boldsymbol{\theta}}>0,\  \alpha^{\boldsymbol{w}}>0$ and discount factor $\gamma \in [0,1]$\;
 Initialize policy and state-value parameters $\boldsymbol{\theta}\in\mathbb{R}^d$ and $\boldsymbol{w}\in\mathbb{R}^{d'}$\;
 \For{Episode = 1, 2, ...}{
  \While{$S_t$ is not terminal (for each time step $t$)}{
    Sample action $A_t \sim \pi(\cdot|S_t;\boldsymbol{\theta})$ \;
    Take action $A_t$ and observe $S_{t+1}, R_{t+1}$\;
    \If{$S_{t+1}$ is terminal}{
      $V(S_{t+1}; \boldsymbol{w}) = 0$\;
    }
    $\delta \gets R_{t+1} + \gamma V(S_{t+1}; \boldsymbol{w}) - V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{w} \gets \boldsymbol{w} + \alpha^{\boldsymbol{w}} \delta \nabla V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{\theta} \gets \boldsymbol{\theta} + \alpha^{\boldsymbol{\theta}} \delta \nabla \log{\pi(A_{t}|S_{t}; \boldsymbol{\theta})}$\;
    $S_t \gets S_{t+1}$\;
  }
 }
 \caption{Advantage Actor Critic pseudocode \cite{Sutton1998}.}
 \label{alg:A2C}
\end{algorithm}
%}

@@

\begin{equation}
  J(\boldsymbol{\theta}) - \eta D_{KL}(\pi_{\theta_{old}} || \pi_{\eta})
\end{equation}

>>>>

\noindent This interaction  is an example of a Markov Decision Process (MDP)\cite{Sutton1998} $\mathcal{M}=<\mathcal{S}, \mathcal{A}, P, R>$, where:

@@

Now that we have (more or less) a clear idea of what RL seeks (maximize the return $G$) and how to do it (by finding an optimal policy $\pi$), we need to define a way to quantify how good a state $s$ is (in terms of the return $G$) in a given environment (when we follow a policy $\pi$), and how good an action $a$ is (in terms of the return $G$) when the environment is in state $s$ (and when we follow a policy $\pi$). This is done through the \emph{State-value} and \emph{Action-value} functions respectively:
\begin{itemize}
    \item \textbf{State-value}: $V_{\pi}(s):= \mathbb{E}_{\pi}[G_t|s_t=s]$.
    \item \textbf{Action-value}: $Q_{\pi}(s, a):= \mathbb{E}_{\pi}[G_t|s_t=s, a_t=a]$.
\end{itemize}

@@

\begin{equation*}
  \resizebox{1\linewidth}{!}{%
  $
    \boldsymbol{\theta}_{t+1} = \boldsymbol{\theta}_{t} + \alpha (R_{t+1} + \gamma V(S_{t+1};\boldsymbol{w}) - V(S_{t};\boldsymbol{w})) \nabla \log{\pi (A_t|S_t; \boldsymbol{\theta})}
  $
  }
  %\label{eq:learn_rule_4}
\end{equation*}

But, what about the update rule for the state-value function $V(S;\boldsymbol{w})$ parameters $\boldsymbol{w}$? As we did with the policy, we need to start by defining an objective function $E(\boldsymbol{w})$. Since $V: \mathbb{R} \rightarrow \mathbb{R}$ (regression problem), we can just use the \emph{Squared Error} as a loss function (i.e. $E(\boldsymbol{w}):=(V_{\pi}(S) - V(S;\boldsymbol{w}))^2$), and then optimize the approximator parameters $\boldsymbol{w}$ while minimizing it. Therefore:

\begin{equation*}
  \begin{split}
    \nabla E(\boldsymbol{w}) &= \nabla (V_{\pi}(S_t) - V(S_t;\boldsymbol{w}))^2 \\
    &= 2(V_{\pi}(S_t)) - V(S_t;\boldsymbol{w})) \nabla V(S_t;\boldsymbol{w})) \\
    &\approx 2(R_{t+1} + \gamma V(S_{t+1};\boldsymbol{w}) - V(S_t;\boldsymbol{w})) \nabla V(S_t;\boldsymbol{w}))
  \end{split}
\end{equation*}

Therefore, the update rule for $\boldsymbol{w}$ is:

\begin{equation*}
  \resizebox{1\linewidth}{!}{%
  $
    \boldsymbol{w}_{t+1} = \boldsymbol{w}_t - \alpha (R_{t+1} + \gamma V(S_{t+1}; \boldsymbol{w}) - V(S_{t}; \boldsymbol{w})) \nabla V(S_{t}; \boldsymbol{w})
    $
  }
  %\label{eq:learn_rule_w}
\end{equation*}

A pseudocode for an algorithm which approximate both the policy and the state-value function is shown in \ref{alg:A2C}.

%\resizebox{.95\linewidth}{!}{%
\begin{algorithm}[h]
 \textbf{Input}: differentiable policy and state-value function parameterization $\pi(a|s;\boldsymbol{\theta})$ and $V(s;\boldsymbol{w})$\;
 \textbf{Parameters}: step sizes $\alpha^{\boldsymbol{\theta}}>0,\  \alpha^{\boldsymbol{w}}>0$ and discount factor $\gamma \in [0,1]$\;
 Initialize policy and state-value parameters $\boldsymbol{\theta}\in\mathbb{R}^d$ and $\boldsymbol{w}\in\mathbb{R}^{d'}$\;
 \For{Episode = 1, 2, ...}{
  \While{$S_t$ is not terminal (for each time step $t$)}{
    Sample action $A_t \sim \pi(\cdot|S_t;\boldsymbol{\theta})$ \;
    Take action $A_t$ and observe $S_{t+1}, R_{t+1}$\;
    \If{$S_{t+1}$ is terminal}{
      $V(S_{t+1}; \boldsymbol{w}) = 0$\;
    }
    $\delta \gets R_{t+1} + \gamma V(S_{t+1}; \boldsymbol{w}) - V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{w} \gets \boldsymbol{w} - \alpha^{\boldsymbol{w}} \delta \nabla V(S_{t}; \boldsymbol{w})$\;
    $\boldsymbol{\theta} \gets \boldsymbol{\theta} + \alpha^{\boldsymbol{\theta}} \delta \nabla \log{\pi(A_{t}|S_{t}; \boldsymbol{\theta})}$\;
    $S_t \gets S_{t+1}$\;
  }
 }
 \caption{Advantage Actor Critic pseudocode \cite{Sutton1998}.}
 \label{alg:A2C}
\end{algorithm}
%}

@@

\begin{equation}
  J(\boldsymbol{\theta}) - \eta D_{KL}(\pi_{\theta_{old}} || \pi_{\theta})
\end{equation}
